---
title: "Markup"
author: "Miguel Angel Bustos"
date: "14-01-2022"
output:
  pdf_document: default
  html_document: default
---
**Introduction**

The basic rule of a successful business model is to sell a product or service for more than it costs to produce or provide it. The Markup or markon it´s the difference between the cost of a product or service and its sale price and can be calculated in your local currency or as a percentage of either cost or selling price.


```{r include=FALSE}
knitr::opts_chunk$set(comment = NA)
```

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)

```

One coffe cost and it´s markup

```{r}
one_coffe_cost <- 800
one_coffe_sell <- 1000
one_coffe_ratio <- 200
one_coffe_markup <- one_coffe_ratio/one_coffe_cost*100

per_coffe_markup <- data.frame(one_coffe_cost = c(800),
                   one_coffe_sell = c(1000),
                   one_coffe_ratio = c(one_coffe_sell-one_coffe_cost),
                   one_coffe_markup = c(one_coffe_ratio/one_coffe_cost*100))
per_coffe_markup
```

**Plotting the coffe markup**

This is the one coffe markup, reduce costs per coffe to obtain a major markup, now the strategy for this situation is how to do that, good negotiations or extended contracts are just of many options that can be evaluated.

```{r}
boxplot(per_coffe_markup, notch = TRUE, border = "Orange", ylim = c(0,4400))
```

**p*q price per quantity**

The formula for revenue it´s p*q and here are some vectors of one coffe values:

```{r}

c <- 800 # cost (one_coffe_cost)
p <- 1000 # p price (one_coffe_sell)
q <- 5500 # q quantity or revenue

```


**Weekly sales**

Now the week sales situation it´s 5500 coffes were sold, now this is the gross profit and week markup

```{r}

COGS <- q*c # Cost of goods sold 4.400.000
COGS
revenue <- p*q # 5.500.000
revenue
Gross_Profit <- revenue - COGS # 5.500.000 - 4.400.000
Gross_Profit
Gross_Profit/COGS # This is the week markup

```

*The week markup*

Now the data it´s well ordered in the week, obtaining a 25% markup, that´s a good markdown

```{r}

week_markup <- data.frame(c_cost = c(800),
                   p_price = c(1000),
                   q_quantity = c(5500),
                   COGS = c(q*c),
                   revenue = c(p*q),
                   gross_profit = c(revenue - COGS),
                   weekmarkup = c(100*(revenue-COGS)/COGS))
week_markup

```

**Ploting the markup week**

Now this is the markup visualization sales week

```{r}

boxplot(week_markup %>% select("COGS", "revenue", "gross_profit", "weekmarkup"), 
        norch = T, 
        border = c("Blue", "Green", "Yellow", "Red"),
        main = "Week Summary : 25% of Markup",
        ylab = "length",
        xlab = "Concept",
        ylim = c(0,44000000), notch = T, las = 1, names = c("Cost of Goods", "Revenue", "Profit", "Markup")) #las 1 or 2

```



        
